Mathematical appendix to "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2022-07-09 src/docs_paper/appendix.Rmd
Improving appendix (mostly some text about coverage) #128

Let $i \in \{1, \ldots, n\}$ denote subnational units (Table B.5) which partition the 13 studied AGYW priority countries $c[i] \in \{1, \ldots, 13\}$.
We considered the years 1999-2018 denoted as $t \in \{1, \ldots, T\}$ and age groups $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$.
Let the four risk groups be $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
We used a multinomial logistic regression model to infer the proportion of AGYW in the risk groups $k \in \{1, 2, 3^{+}\}$.
This model can be specified using a multinomial likelihood
\begin{equation}
    \y_{ita} = (y_{ita1}, \ldots, y_{ita3^{+}})^\top \sim \text{Multinomial}(m_{ita}; \, p_{ita1}, \ldots, p_{ita3^{+}}),
\end{equation}
where the number of women in risk group $k$ is $y_{itak}$, the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, and $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
Following the baseline category approach with $k = 1$, linear predictors may then be specified for the additive log ratios $\log(p_{itak} / p_{ita1})$.
To facilitate inference in the `R-INLA`, we used an equivalent Poisson log-linear model via the multinomial-Poisson transformation [@baker1994multinomial].
This transformation, and further details about this model, are presented in Section 1.2.

Next, we fit a logistic regression model to estimate the proportion of those in the $k = 3^{+}$ risk group that were in the $k = 3$ and $k = 4$ risk groups respectively.
This model was of the form
\begin{align}
    y_{ia4} &\sim \text{Binomial} \left( y_{ia3} + y_{ia4}, q_{ia} \right), \label{eq:logistic-regression} \\
    q_{ia} &= \text{logit}^{-1} \left( \eta_{ia} \right), 
\end{align}
where $q_{ia} = p_{ia4} / (p_{ia3} + p_{ia4}) = p_{ia4} / p_{ia{3^+}}$ and the linear predictor $\eta_{ia}$ is chosen suitably, described in Section 1.3.
Taking this two-step approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question in Equation \ref{eq:logistic-regression}.
As all such surveys occurred in 2013-2018, in the logistic regression model $q_{ia}$ was assumed to be constant over time.

To facilitate uncertainty quantification, we took 1000 posterior samples, indexed by $s$, from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via $p_{ita3}^s = (1 - q_{ia}^s)p_{ita{3^+}^s}$ and $p_{ita4}^s = q_{ia}^s p_{ita{3^+}}^s$.

As transactional sex does not directly correspond to sex work [@wamoyi2016transactional], we adjusted our samples so that at a national level, the population size estimates match FSW population size estimates at a national level by age.
Our methodology for producing these estimates is described in Section \ref{fsw-population-size-estimation}.
In making this adjustment, we assumed that subnational variation in the FSW proportion corresponds to that of the transactional sex proportion.

@@

We considered eight models (Table \ref{tab:multinomial-models}) for $\eta_{ita}$ of the form
$$
\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{c[i]k} + \phi_{ik} + \gamma_{tk} + \delta_{itk}.
$$
As described above, we included observation random effects in all models we considered, and set $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$.
To capture country-specific proportion estimates for each category, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
Heterogeneity in risk group proportions by age was allowed by including age-country-category random effects $\alpha_{ack} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
We considered two specifications, independent and identically distributed (IID) and Besag, for the space-category $\phi_{ik}$ random effects (Section \ref{sec:spatial-random-effects}) and two specifications, IID and first order autoregressive (AR1), for the year-category $\gamma_{tk}$ random effects (Section \ref{sec:temporal-random-effects}).
We also considered separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure (Section \ref{sec:spatio-temporal-random-effects}).

All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma\, \tau_\delta\}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$ where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.

#### Spatial random effects \label{sec:spatial-random-effects}

The specifications we considered were IID $\phi_{ik} \sim \mathcal{N}(0, \tau_\phi^{-1})$ and Besag grouped by category
$$
\bphi = (\phi_{11}, \ldots, \phi_{n1}, \ldots, \phi_{13^{+}}, \ldots \phi_{n3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\phi)^{-})
$$
where the scaled structure matrix $\mathbf{R}^\star_\phi = \mathbf{R}^\star_b \otimes \mathbf{I}$ is given by the Kronecker product of the scaled Besag structure matrix $\mathbf{R}^\star_b$ and the identity matrix $\mathbf{I}$, and ${-}$ denotes the generalised matrix inverse.
Scaling of the structure matrix to have generalised variance one ensures interpretable priors may be placed on the precision parameter [@sorbye2014scaling].
We followed the further recommendations of @freni2018note with regard to disconnected adjacency graphs, singletons and constraints.
The Besag structure matrix $\mathbf{R}_b$ is obtained by the precision matrix of the random effects $\mathbf{b} = (b_1, \ldots, b_n)^\top$ with the full conditionals
\begin{equation}
b_i \, | \, \mathbf{b}_{-i} \sim \N\left(\frac{\sum_{j: j \sim i} b_j}{n_{\delta i}}, \frac{1}{n_{\delta i}}\right),
\end{equation}
where $j \sim i$ if the districts $A_i$ and $A_j$ are adjacent, and $n_{\delta i}$ is the number of districts adjacent to $A_i$.

In preliminary testing, we excluded spatial random effects from the model, but found that this negatively effected performance.
We also tested using the BYM2 model [@simpson2017penalising] in place of the Besag, but found that the proportion parameter posteriors tended to be highly peaked at the value one so for simplicity and to avoid numerical issues, by using Besag random effects we decided to fix this proportion to one.

#### Temporal random effects \label{sec:temporal-random-effects}

The specifications we considered were IID $\phi_{tk} \sim \mathcal{N}(0, \tau_\phi^{-1})$ and AR1 grouped by category
$$
\bm{\gamma} = (\gamma_{11}, \ldots, \gamma_{13^{+}}, \ldots, \gamma_{T1}, \ldots, \gamma_{T3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\gamma)^{-})
$$
where the scaled structure matrix $\mathbf{R}^\star_\gamma = \mathbf{R}^\star_r \otimes \mathbf{I}$ is given by the Kronecker product of a scaled AR1 structure matrix $\mathbf{R}^\star_r$ and the identity matrix $\mathbf{I}$.
The AR1 structure matrix $\mathbf{R}_r$ is obtained by precision matrix of the random effects $\mathbf{r} = (r_1, \ldots, r_T)^\top$ specified by
\begin{align}
r_1 &\sim \left( 0, \frac{1}{1 - \rho^2} \right), \\
r_t &= \rho r_{t - 1} + \epsilon_t, \quad t = 2, \ldots, T, 
\end{align}
where $\epsilon_t \sim \mathcal{N}(0, 1)$ and $|\rho| < 1$.
For the lag-one correlation parameter $\rho$, we used the PC prior, as derived by @sorbye2017penalised, with base model $\rho = 1$ and condition $\mathbb{P}(\rho > 0 = 0.75)$.
We chose a base model corresponding to no change in behaviour over time, rather than the alternative $\rho = 0$ corresponding to no correlation in behaviour over time, as we judged the former to be more plausible a priori.

#### Spatio-temporal random effects \label{sec:spatio-temporal-random-effects}

We used the specification
\begin{equation}
    \bm{\delta} = (\delta_{111}, \ldots, \delta_{nT3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\delta \mathbf{R}^\star_\delta)^{-}),
\end{equation}
where $\mathbf{R}^\star_\delta$ is a Kronecker product of the relevant space, time and category structure matrices.
In particular, for each of the four models including spatio-temporal interactions, these matrices are
\begin{itemize}
\item
1x: No spatial or temporal structure (Type I) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{I} \otimes \mathbf{I}$,
\item
2x: Structured spatial and unstructured temporal (Type II) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{I} \otimes \mathbf{I}$,
\item
3x: Unstructured spatial and structured temporal (Type III) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
\item
4x: Structured spatial and temporal (Type IV) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
\\
\end{itemize}
where the first, second and third elements of the product represent space, time and category respectively, and the interaction type provided in brackets is given according to the @knorr2000bayesian framework.

#### Constraints

To ensure interpretable posterior inferences of random effect contribution, we applied sum-to-zero constraints such that the country-category, age-country-category, space-category and year-category random effects did not alter overall category probabilities.
For the space-year-category random effects, we analogously applied sum-to-zero constraints to maintain roles of the space-category and year-category random effects.
Together, these were:
\begin{enumerate}
    \item Category $\sum_k \beta_k = 0$
    \item Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
    \item Age-country $\sum_a \alpha_{ack} = 0, \, \forall \, c, k$,
    \item Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$
    \item Temporal $\sum_t \gamma_{tk} = 0, \, \forall \, k$
    \item Spatio-temporal\footnote{The constraints for the space-year-category random effects were unable to be implemented fully, though this only effects the variance components interpretation.} $\sum_i \delta_{itk} = 0, \, \forall \, t, k;
\quad \sum_t \delta_{itk} = 0, \, \forall \, i, k;
\quad \sum_k \delta_{itk} = 0, \, \forall \, i, t$
\end{enumerate}

@@

The surveys we included use a complex design, in which each individual has an unequal probability of being included in the sample.
For example, the DHS often employs a two-stage cluster design, first taking an urban rural stratified sample of ennumeration areas, before selecting households from each ennumeration area using systematic sampling [@measure2012sampling].
To account for the survey design, we use a weighted pseudo-likelihood where the observed counts $y$ are replaced by effective counts $y^\star$ calculated using the survey weights $w_j$ of all individuals $j$ in the corresponding strata.
We multiplied direct estimates produced using the `survey` package [@JSSv009i08] by the Kish effective sample size [@kish1965survey]
\begin{equation}
    m^\star = \frac{\left(\sum_j w_j \right)^2}{\sum_j {w_j}^2}
\end{equation}
to obtain $y^\star$.
These counts may not be integers, and the Poisson likelihood we used in Equation \ref{eq:poisson} is inappropriate.
Instead, we used a generalised Poisson pseudo-likelihood $y^\star \sim \text{xPoisson}(\kappa)$, given by
\begin{equation}
    p(y^\star) = \frac{\kappa^{y^\star}}{\left \lfloor{y^\star!}\right \rfloor } \exp \left(- \kappa \right),
\end{equation}
as implemented by `family = "xPoisson"` in `R-INLA`.

@@

To fill: explanation of Figure \ref{fig:coverage}.

\begin{figure}
  \centering
  \makebox[\textwidth][c]{\includegraphics{depends/coverage.png}}
  \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the final selected models. These plots are adapted from \citet{sailynoja2021graphical} and are an example of posterior predictive checks, see for example \citet[Chapter 6.1]{gelman2020bayesian}.}
  \label{fig:coverage}
\end{figure}

>>>>

Let $i \in \{1, \ldots, n\}$ denote subnational units (Table B.5) which partition the 13 studied AGYW priority countries $c[i] \in \{1, \ldots, 13\}$.
We considered the years 1999-2018 denoted as $t \in \{1, \ldots, T\}$ and age groups $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$.
Let the four risk groups be $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.

First, we used a multinomial logistic regression model to infer the proportion of AGYW in the risk groups $k \in \{1, 2, 3^{+}\}$.
This model can be specified using a multinomial likelihood
\begin{equation}
    \y_{ita} = (y_{ita1}, \ldots, y_{ita3^{+}})^\top \sim \text{Multinomial}(m_{ita}; \, p_{ita1}, \ldots, p_{ita3^{+}}),
\end{equation}
where the number of women in risk group $k$ is $y_{itak}$, the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, and $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
Taking $k = 1$ to be the baseline category, linear predictors may be specified for the additive log ratios $\log(p_{itak} / p_{ita1})$.
Rather than taking this approach directly, to facilitate inference in the `R-INLA`, we used an equivalent Poisson log-linear model via the multinomial-Poisson transformation [@baker1994multinomial].
This transformation, and further details about this model, are presented in Section 1.2.

Next, we fit a logistic regression model to estimate the proportion of those in the $k = 3^{+}$ risk group that were in the $k = 3$ and $k = 4$ risk groups respectively.
This model was of the form
\begin{align}
    y_{ia4} &\sim \text{Binomial} \left( y_{ia3} + y_{ia4}, q_{ia} \right), \label{eq:logistic-regression} \\
    q_{ia} &= \text{logit}^{-1} \left( \eta_{ia} \right), 
\end{align}
where $q_{ia} = p_{ia4} / (p_{ia3} + p_{ia4}) = p_{ia4} / p_{ia{3^+}}$ and the linear predictor $\eta_{ia}$ is chosen suitably, described in more detail in Section 1.3.
Taking this two-step approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question in Equation \ref{eq:logistic-regression}.
As all such surveys occurred in 2013-2018, in the logistic regression model $q_{ia}$ was assumed to be constant over time.

To facilitate uncertainty quantification, we took 1000 posterior samples (indexed by $s$) from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via $p_{ita3}^s = (1 - q_{ia}^s)p_{ita{3^+}^s}$ and $p_{ita4}^s = q_{ia}^s p_{ita{3^+}}^s$.

As transactional sex does not directly correspond to sex work [@wamoyi2016transactional], we adjusted our samples so that at a national level, the population size estimates match FSW population size estimates at a national level by age.
Our methodology for producing these estimates is described in Section \ref{fsw-population-size-estimation}.
In making this adjustment, we assumed that subnational variation in the FSW proportions corresponds to that of the transactional sex proportions.

@@

We considered eight models (Table \ref{tab:multinomial-models}) for $\eta_{ita}$ of the form
$$
\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{c[i]k} + \phi_{ik} + \gamma_{tk} + \delta_{itk}.
$$
As described above, we included observation random effects $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$ in all models we considered.
To capture country-specific proportion estimates for each category, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
Heterogeneity in risk group proportions by age was allowed by including age-country-category random effects $\alpha_{ack} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
We considered two specifications, independent and identically distributed (IID) and Besag [@besag1991bayesian], for the space-category $\phi_{ik}$ random effects (Section \ref{sec:spatial-random-effects}) and two specifications, IID and first order autoregressive (AR1), for the year-category $\gamma_{tk}$ random effects (Section \ref{sec:temporal-random-effects}).
We also considered separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure (Section \ref{sec:spatio-temporal-random-effects}).
All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma\, \tau_\delta\}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$ where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.

### Spatial random effects \label{sec:spatial-random-effects}

The specifications we considered were IID
$$
\phi_{ik} \sim \mathcal{N}(0, \tau_\phi^{-1}),
$$
and Besag grouped by category
$$
\bphi = (\phi_{11}, \ldots, \phi_{n1}, \ldots, \phi_{13^{+}}, \ldots \phi_{n3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\phi)^{-}),
$$
where the scaled structure matrix $\mathbf{R}^\star_\phi = \mathbf{R}^\star_b \otimes \mathbf{I}$ is given by the Kronecker product of the scaled Besag structure matrix $\mathbf{R}^\star_b$ and the identity matrix $\mathbf{I}$, and ${-}$ denotes the generalised matrix inverse.
Scaling of the structure matrix to have generalised variance one ensures interpretable priors may be placed on the precision parameter [@sorbye2014scaling].
We followed the further recommendations of @freni2018note with regard to disconnected adjacency graphs, singletons and constraints.
The Besag structure matrix $\mathbf{R}_b$ is obtained by the precision matrix of the random effects $\mathbf{b} = (b_1, \ldots, b_n)^\top$ with full conditionals
\begin{equation}
b_i \, | \, \mathbf{b}_{-i} \sim \N\left(\frac{\sum_{j: j \sim i} b_j}{n_{\delta i}}, \frac{1}{n_{\delta i}}\right),
\end{equation}
where $j \sim i$ if the districts $A_i$ and $A_j$ are adjacent, and $n_{\delta i}$ is the number of districts adjacent to $A_i$.

In preliminary testing, we excluded spatial random effects from the model, but found that this negatively effected performance.
We also tested using the BYM2 model [@simpson2017penalising] in place of the Besag, but found that the proportion parameter posteriors tended to be highly peaked at the value one.
For simplicity and to avoid numerical issues, by using Besag random effects we decided to fix this proportion to one.

### Temporal random effects \label{sec:temporal-random-effects}

The specifications we considered were IID
$$
\phi_{tk} \sim \mathcal{N}(0, \tau_\phi^{-1}),
$$
and AR1 grouped by category
$$
\bm{\gamma} = (\gamma_{11}, \ldots, \gamma_{13^{+}}, \ldots, \gamma_{T1}, \ldots, \gamma_{T3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\gamma)^{-}),
$$
where the scaled structure matrix $\mathbf{R}^\star_\gamma = \mathbf{R}^\star_r \otimes \mathbf{I}$ is given by the Kronecker product of a scaled AR1 structure matrix $\mathbf{R}^\star_r$ and the identity matrix $\mathbf{I}$.
The AR1 structure matrix $\mathbf{R}_r$ is obtained by precision matrix of the random effects $\mathbf{r} = (r_1, \ldots, r_T)^\top$ specified by
\begin{align}
r_1 &\sim \left( 0, \frac{1}{1 - \rho^2} \right), \\
r_t &= \rho r_{t - 1} + \epsilon_t, \quad t = 2, \ldots, T, 
\end{align}
where $\epsilon_t \sim \mathcal{N}(0, 1)$ and $|\rho| < 1$.
For the lag-one correlation parameter $\rho$, we used the PC prior, as derived by @sorbye2017penalised, with base model $\rho = 1$ and condition $\mathbb{P}(\rho > 0 = 0.75)$.
We chose the base model $\rho = 1$ corresponding to no change in behaviour over time, rather than the alternative $\rho = 0$ corresponding to no correlation in behaviour over time, as we judged the former to be more plausible a priori.

### Spatio-temporal random effects \label{sec:spatio-temporal-random-effects}

We used the specification
\begin{equation}
    \bm{\delta} = (\delta_{111}, \ldots, \delta_{nT3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\delta \mathbf{R}^\star_\delta)^{-}),
\end{equation}
where $\mathbf{R}^\star_\delta$ is a Kronecker product of the relevant space, time and category structure matrices.
In particular, for each of the four models including spatio-temporal interactions, these matrices are

1. No spatial or temporal structure (Type I) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{I} \otimes \mathbf{I}$,
2. Structured spatial and unstructured temporal (Type II) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{I} \otimes \mathbf{I}$,
3. Unstructured spatial and structured temporal (Type III) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
4. Structured spatial and temporal (Type IV) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,

where the first, second and third elements of the Kronecker product represent space, time and category strucutre matrices respectively.
The interaction type in brackets (e.g. Type I) is given according to the @knorr2000bayesian framework.

### Constraints

To ensure interpretable posterior inferences of random effect contribution, we applied sum-to-zero constraints such that none of the category interaction random effects altered overall category probabilities.
For the space-year-category random effects, we applied analogous sum-to-zero constraints to maintain roles of the space-category and year-category random effects.
Together, these were:

1. Category $\sum_k \beta_k = 0$
2. Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
3. Age-country $\sum_a \alpha_{ack} = 0, \, \forall \, c, k$,
4. Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$
5. Temporal $\sum_t \gamma_{tk} = 0, \, \forall \, k$
6. Spatio-temporal\footnote{It was not possible to fully implement these constraints in \texttt{R-INLA}. This only effects the variance components interpretation.} $\sum_i \delta_{itk} = 0, \, \forall \, t, k;
\quad \sum_t \delta_{itk} = 0, \, \forall \, i, k;
\quad \sum_k \delta_{itk} = 0, \, \forall \, i, t$

@@

The surveys we included use a complex design, in which each individual has an unequal probability of being included in the sample.
The DHS [@measure2012sampling], for example, often employs a two-stage cluster design, first taking an urban rural stratified sample of ennumeration areas, before selecting households from each ennumeration area using systematic sampling.

To account for this aspect of survey design, we use a weighted pseudo-likelihood where the observed counts $y$ are replaced by effective counts $y^\star$ calculated using the survey weights $w_j$ of all individuals $j$ in the corresponding strata.
We multiplied direct estimates produced using the `survey` package [@JSSv009i08] by the Kish effective sample size [@kish1965survey]
\begin{equation}
    m^\star = \frac{\left(\sum_j w_j \right)^2}{\sum_j {w_j}^2}
\end{equation}
to obtain $y^\star$.
These counts may not be integers, and as such the Poisson likelihood we used in Equation \ref{eq:poisson} is not appropriate.
Instead, we used a generalised Poisson pseudo-likelihood $y^\star \sim \text{xPoisson}(\kappa)$, given by
\begin{equation}
    p(y^\star) = \frac{\kappa^{y^\star}}{\left \lfloor{y^\star!}\right \rfloor } \exp \left(- \kappa \right),
\end{equation}
as implemented by `family = "xPoisson"` in `R-INLA`, which accepts non-integer input.

@@

To assess the calibration of our fitted model, we calculated the quantile $q$ of each observation within the posterior predictive distribution (that is, within the collection of samples generated from the posterior predictive distribution).
For calibrated models, these quantiles, known as probability integral transform (PIT) values [@dawid1984present; @bosse2022scoringutils], should follow a uniform distribution $q \sim \mathcal{U}[0, 1]$.

Using the PIT values, it is possible to calculate the empirical coverage of all $(1 - \alpha)100$\% (equal-tailed) posterior predictive credible intervals.
These empirical coverages can be compared to the nominal coverage $(1 - \alpha)$ for each value of $\alpha \in [0, 1]$ to give empirical cumulative distribution function (ECDF) difference values.
This approach has the advantage of considering all possible confidence values at once.
@sailynoja2021graphical develop binomial distribution-based simultaneous confidence bands for ECDF difference values which test uniformity.

Figure \ref{fig:coverage} shows the PIT histogram and ECDF difference plots for our final model, faceted by risk group.
<!-- Comment on the results. -->
<!-- What is going on with the cohabiting partner group towards one? -->

\begin{figure}
  \centering
  \makebox[\textwidth][c]{\includegraphics{depends/coverage.png}}
  \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the final selected model.}
  \label{fig:coverage}
\end{figure}
